{\tt APFELgrid}: a fast interface to hadronic observables for fits of parton densities

### 2016-04-20 paper.tex
editing the paper

The need for fast and accurate cross-section predictions in the Large
Hadron Collider (LHC) era is becoming increasingly important. In fact,
the outstanding amount of precise data produced by the LHC experiments
is bound to provide a very stringent constraint on the proton parton
distribution functions (PDFs) on the condition that as many
measurements as possible are included in PDF fits with the highest
accuracy possible. However, the direct use of most of the codes that
provide predictions for non-inclusive hadron-collider observables in a
PDF fit, which typically requires a large number of iterations, is not
viable because the time required to obtain accurate predictions is
usually of the order of a few hours or more. In order to overcome this
limitation, the typical strategy adopted relies on the precomputation
of the partonic hard cross sections in such a way that the numerical
convolution with any set of PDFs can be quickly performed {\it a
  posteriori} by means of interpolation techniques. Examples of the
implementation of such a strategy are {\tt
  APPLgrid}~\cite{Carli:2010rw} and {\tt
  FastNLO}~\cite{Wobisch:2011ij}.

>>>>

The need for fast and accurate cross-section predictions in the Large
Hadron Collider (LHC) era is becoming increasingly important. In fact,
the outstanding amount of precise data produced by the LHC experiments
is bound to provide a very stringent constraint on the proton parton
distribution functions (PDFs) on the condition that as many
measurements as possible are included in PDF fits with the highest
accuracy possible. However, the direct use of most of the codes that
provide predictions for non-inclusive hadron-collider observables in a
PDF fit, which typically requires a large number of iterations, is not
viable because the time required to obtain accurate predictions is
usually of the order of a few hours or more. In order to overcome this
limitation, the typical strategy adopted relies on the precomputation
of the partonic hard cross sections in such a way that the numerical
convolution with any set of PDFs can be quickly performed {\it a
  posteriori} by means of interpolation techniques. Examples of the
implementation of this strategy are {\tt APPLgrid}~\cite{Carli:2010rw}
and {\tt FastNLO}~\cite{Wobisch:2011ij}. For the computation of the
hard cross sections, these packages rely on external codes to which
they are interfaced, more or less directly, by means of a suite of
functions whose scope is that of filling up PDF- and
$\alpha_s$-independent lookup tables of cross-section weights that can
subsequently be combined with an arbitrary PDF set. Examples of codes that have been directly interfaced to
